Dynamic Topic Modeling for Voice Dialogues

### 2024-05-14 paper/main.tex
change pipeline and metrics

\subsection{ASR}

Word Error Rate (WER) is the metric for speech recognition. This metric counts errors at the word level. 
A substitutions (S), insertions (I) and deletions (D) error are counted for each word. \\
For example:

\begin{figure}[h]
    \includegraphics[scale=1]{img/wer.png}
\end{figure}

Word "sat" predicted as "sit", it is substitutions error, and the word "mat" and was not recognized at all, it is deletion error.\\
To calculate the metric, take the formula:

$WER = \frac{S + I + D}{N}$, \\
where N is total number of words in the example.

Note that the word "sit" has only one incorrect character, but the whole word is marked as incorrect.
This is a defining feature of the WER: spelling errors are heavily penalised, no matter how minor.

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

>>>>

\subsection{Speaker diarization}

The standard metric for speaker diarization problem is the Diarization error rate \:
This metric computes the error in diarization in terms of a duration ratio, which means that a perfectly aligned hypothesis and reference diarization would result in DER=0. It sums up 3 error:
\begin{itemize}
    \item False Alarm - speech segment predicted where there is no speaker. It is error from ASR models.
    \item Missed Detection - no speech detected where there is a speaker. It is error from ASR models.
    \item Confusion	Speech - the wrong cluster. It is error from the clustering model
\end{itemize}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.8]{img/der.png}
    \caption{Diarization error rate }
\end{figure}

Mathematically, the metric can be written: 
\begin{center}
    $DER = \frac{False Alarm  +  Missed Detection  +  Confusion}{Total}$    
\end{center}

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & null \\ 
            \hline
            Product Meetings (QMSum) & 137 & 535.6 & null \\ 
            Academic Meetings (QMSum) & 59 & 819.0 & null \\ 
            Comemitie Meetings (QMSum) & 36 & 207.7 & null \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |} 
        \hline
        \multicolumn{1}{| c |}{} & \multicolumn{3}{| c |}{Product} &  \multicolumn{3}{| c |}{Academic} & \multicolumn{3}{| c |}{Committee} \\
        \hline
        model  & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        whisper-large +  &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        bert-base CLS &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1  \\ 
        bert-large NSP & Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        opt-128 &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        dialoGPT-medium &  Pk & wd & f1 & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
    \end{tabular}
\end{center}
